Applicability of SSM and UML for Designing a Search Application for the British Broadcasting Corporation (BBC)

### 2014-06-10 talk.tex
Half way through the headings now.

\usetheme{Pittsburgh}
\usecolortheme{beaver}

@@

@@

\title{Building a Web Search}
\author{Ross Fenning}
\institute{
  Senior Software Engineer
  \\Content Discovery
  \\Future Media
  \\BBC
}
\date{17 June, 2014}

@@

% Design Goals
\begin{frame}
  \frametitle{Design Goals}
  \begin{itemize}
    \pause \item Existing search application serves a wide variety of use cases
    \pause \item Start high-level thinking and design of a new search application
    \pause \item Take a ``fresh'' approach as if we are replacing the whole system
    \pause \item A new design can (hopefully) inform iterative improvements on a current system
    \pause \item Can SSM give us contextualisation that applies both to a new application and to existing systems?
    \pause \item The Search application should integrate where possible with other existing systems
    \pause \item Can SSM helps us consider the holistic search system that emerges after this integration?
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Problem Contextualisation through SSM}
  \framesubtitle{Rich Picture}
  \includegraphics[width=\linewidth]{rich-picture.png}
\end{frame}

% Extracting use cases
\begin{frame}
  \frametitle{Use Case Extraction}
  \framesubtitle{Identifying users}
  \begin{itemize}
    \pause \item Identifier all users of the system in the rich picture
    \pause \item Separate \emph{direct} users from \emph{meta-level} users
    \pause \item Direct use cases should emerge from the rich picture
    \pause \item This separation is still \emph{subjective} and use cases may change as the rich picture changes
  \end{itemize}
\end{frame}

@@

% Domain modelling for search -- model business rules as per benefits shown in background, but also keep it generic
% Discussion and Analysis -- Use cases - More SSM needed?
% Discussion and Analysis -- Domain Model -- Polymorphism
% Discussion and Analysis -- Domain Model -- Duck Typing
% Discussion -- More SSM: 3 Es?
% Shortcomings -- Performance? NFRs?
% Shortcomings -- Agile?
% Validation?

>>>>

\usetheme{Frankfurt}
\usecolortheme{seagull}

@@

\def\email#1{{\tt#1}}

@@

\title{Applicability of SSM and UML for Designing a Search Application for the British Broadcasting Corporation (BBC)}
\author{Ross Fenning\inst{1}
  \and Huseyin Dogan\inst{2}
  \and Keith Phalp\inst{2}}
\institute{BBC, UK \\ \email{Ross.Fenning@bbc.co.uk}
  \and Bournemouth University, UK \\ \email{\{hdogan,kphalp\}@bournemouth.ac.uk}}
\date{2014-06-17}

@@

% Design Goals
\begin{frame}
  \frametitle{Design Goals}
  \begin{itemize}
    \pause \item Existing search application serves a wide variety of use cases
    \pause \item Start high-level thinking and design of a new search application
    \pause \item Take a ``fresh'' approach as if we are replacing the whole system
    \pause \item A new design can (hopefully) inform iterative improvements on a current system
    \pause \item The Search application should integrate where possible with other existing systems
    \pause \item Can SSM give us contextualisation that applies both to a new application and to existing systems?
    \pause \item Can SSM helps us consider the holistic search system that emerges after this integration?
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Problem Contextualisation through SSM}
  \framesubtitle{Rich Picture}
  \pause \includegraphics[width=\linewidth]{rich-picture.png}
\end{frame}

% Extracting use cases
\begin{frame}
  \frametitle{Use Case Extraction}
  \framesubtitle{Identifying users}
  \begin{itemize}
    \pause \item Identify all users of the system in the rich picture
    \pause \item Separate \emph{direct} users from \emph{meta-level} users
    \pause \item Direct use cases should emerge from the rich picture
    \pause \item NOTE: This separation is still \emph{subjective} and use cases may change as the rich picture changes
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Use Case Extraction}
  \framesubtitle{UML Use Case Diagram}
  \pause \includegraphics[width=\linewidth]{use_case.png}
\end{frame}

\begin{frame}
  \frametitle{System Behaviour}
  \framesubtitle{Programmes metadata producer}
  \pause \includegraphics[width=\linewidth]{plant_sequence_producer.png}
\end{frame}

\begin{frame}
  \frametitle{System Behaviour}
  \framesubtitle{Website user}
  \begin{center}
    \pause \includegraphics[height=0.8\textheight]{plant_sequence_user.png}
  \end{center}
\end{frame}

\begin{frame}
  \frametitle{System Behaviour}
  \framesubtitle{Lazy-loading page via AJAX}
  \begin{center}
    \pause \includegraphics[height=0.8\textheight]{plant_sequence_ajax.png}
  \end{center}
\end{frame}

% Domain modelling for search -- model business rules as per benefits shown in background, but also keep it generic
\begin{frame}
  \frametitle{Domain Modelling}
  \begin{itemize}
    \pause \item Use cases identify types of content users want to search
    \pause \item Ontology designs exist for specific content domains, e.g. programmes, sport
    \pause \item A search across all content types needs a model to span all domains
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Domain Modelling}
  \framesubtitle{Class Diagram}
  \pause \includegraphics[width=\linewidth]{plant_model.png}
\end{frame}

% Discussion and Analysis -- Use cases - More SSM needed?
% Discussion and Analysis -- Domain Model -- Polymorphism
% Discussion and Analysis -- Domain Model -- Duck Typing
% Discussion -- More SSM: 3 Es?
% Shortcomings -- Performance? NFRs?
% Shortcomings -- Agile?
% Validation?
